Model_CFU

### 2017-01-11 code/HumanCdGF_cdiff_colonization.Rmd
add IQR to mid-range col level samples

```{r setup environment}
pack_used <- c('randomForest','tidyr','ggplot2','plyr', 'dplyr', 'caret')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

@@

@@

randomized_wo_hilo <- c()
base_wo_hilo_rsq <- c()
for(i in 1:100){
  set.seed(i)
  random_cfu <- sample(cfu_wo_hilo_df$log_cfu_med, 
                       length(cfu_wo_hilo_df$log_cfu_med), replace = F)
  set.seed(seed)
  randomized_wo_hilo_rf <- randomForest(cfu_wo_hilo_df[ , -c(1,2)], random_cfu,
                           ntree = 501,
                           mtry = 15)
  randomized_wo_hilo <- rbind(randomized_wo_hilo, 
                               data.frame(Model = 'Randomized', Observed = random_cfu,
                                          Predicted = randomized_wo_hilo_rf$predicted))
  base_wo_hilo_rsq <- c(base_wo_hilo_rsq, tail(randomized_wo_hilo_rf$rsq,1))
}
set.seed(seed)
cfu_wo_hilo_rf <- randomForest(cfu_wo_hilo_df[ , -2], cfu_wo_hilo_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
top_features_wo_hilo <- head(sort(importance(cfu_wo_hilo_rf)[,1],decreasing = T), n_features)

@@

@@

```{r NMDS of Colonization Level}

full_shared_file <- 'data/process/full_shared.shared'
full_shared_file <- read.table(full_shared_file, sep = '\t', header = T)

>>>>

```{r setup environment}
pack_used <- c('randomForest','tidyr','ggplot2','plyr', 'dplyr', 'caret', 'vegan')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

@@

colonized_cfu_range <- meta_data %>% 
  filter(day %in% c(4:10)) %>% 
  group_by(mouse_id, cage_id, human_source) %>% 
  summarise(log_cfu_med = median(log_cfu),
            low_iqr = quantile(log_cfu)['25%'],
            high_iqr = quantile(log_cfu)['75%']) %>% 
  ungroup()

@@

randomized_wo_hilo <- c()
base_wo_hilo_rsq <- c()
for(i in 1:100){
  set.seed(i)
  random_cfu <- sample(cfu_wo_hilo_df$log_cfu_med, 
                       length(cfu_wo_hilo_df$log_cfu_med), replace = F)
  set.seed(seed)
  randomized_wo_hilo_rf <- randomForest(select(cfu_wo_hilo_df, contains('Otu')), 
                                        random_cfu, ntree = 501, mtry = 15)
  randomized_wo_hilo <-   rbind(randomized_wo_hilo, 
                               data.frame(Model = 'Randomized', Observed = random_cfu,
                                          Predicted = randomized_wo_hilo_rf$predicted))
  base_wo_hilo_rsq <- c(base_wo_hilo_rsq, tail(randomized_wo_hilo_rf$rsq,1))
}
set.seed(seed)
cfu_wo_hilo_rf <- randomForest(select(cfu_wo_hilo_df, contains('Otu')), 
                               cfu_wo_hilo_df$log_cfu_med, ntree = 1001,
                               mtry = 15, importance = T)
top_features_wo_hilo <- head(sort(importance(cfu_wo_hilo_rf)[,1],decreasing = T), n_features)

@@

Furthermore, the variation in the steady state CFU seems to have a high degree of overlap in this middle grouping of colonization level, thus it does not appear possible to precisely define a CFU level to predict relative to the others.

```{r IQR of CFU in middle range, fig.height=4, fig.width=5}
meta_data %>% 
  filter(day %in% c(4:10)) %>% 
  group_by(mouse_id, cage_id, human_source) %>% 
  merge(data.frame(colonized_cfu %>% 
    select(mouse_id, human_source, log_cfu_med) %>% 
    right_join(community_all_d0) %>% 
    filter(!human_source %in% c('DA00581', 'DA01134','DA01146')) %>% 
    filter(!is.na(log_cfu_med)) %>% 
      select(mouse_id), 
                   predicted = cfu_wo_hilo_rf$predicted)) %>% 
  ggplot(aes(x=predicted, y=log_cfu, group=mouse_id))+
     stat_summary(fun.data = 'median_hilow', fun.args=(conf.int=0.5)) + 
     xlim(7,8) + ylim(5,9) +
     labs(x= "Predicted CFU (log10)", y='Observed CFU (log10)\nMedian with IQR of CFU from day 4-10') +
     theme(panel.background = element_rect(linetype = 1, size = 1, fill = 'white', color = 'black'),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank())
```

@@

```{r NMDS of Colonization Level, eval=F}
setwd('~/Documents/Github/Schubert_humanCdGF_XXXX_2016/')
full_shared_file <- 'data/process/full_shared.shared'
full_shared_file <- read.table(full_shared_file, sep = '\t', header = T)
